---
title: "Task 1: Treatment Effect Heterogeneity"
subtitle: "Visual Assessment"
project:
  type: default
  output-dir: results
  execute-dir: project
format:
  html:
    toc: true
    code-fold: false
    embed-resources: true
execute:
  freeze: auto
  echo: true
  warning: false
  message: false
  cache: false
params:
  n_bins: !expr NULL
  min_arm_n: 10L
---

## Setup

```{r}
library(tidyverse)
library(glue)
library(patchwork)
library(knitr)
library(here)
library(fs)

source(here::here("R", "task1_helpers.R"))

results_dir <- here::here("results")
data_dir <- here::here("ressources", "Datasets", "Datasets", "Blinded_data_sets")

csv_files <- get_csv_file_names(data_dir)

csv_files <- csv_files[1:5]

dataset_records <- build_task1_dataset_records(
  csv_files = csv_files,
  n_bins = params$n_bins,
  min_arm_n = params$min_arm_n
)

```

## Scope of this document

This report is restricted to **visual exploration for Task 1**.

It is used to inspect whether treatment effect heterogeneity appears visually plausible within a dataset.

It does **not** perform:

- final variable selection
- patient-level subgroup assignment
- final dataset-level automatic yes or no decisions

Numeric prioritisation is used only to sort and visually mark univariate plots for faster review.

## Manifest und Review-Sheet

```{r}
review_path <- fs::path(results_dir, "task1_visual_review_sheet.csv")

dataset_manifest <- build_dataset_manifest(dataset_records)

task1_review_sheet <- init_task1_review_sheet(
  dataset_manifest = dataset_manifest,
  review_path = review_path
)

knitr::kable(dataset_manifest, format = "pipe")
```

## Dataset triage overview

The table below is a review aid. It helps identify datasets that contain more visually prominent univariate effect patterns. It does not replace the final Task 1 judgement.

```{r}
triage_path <- fs::path(results_dir, "task1_dataset_triage.csv")

task1_dataset_triage <- build_task1_dataset_triage_table(dataset_records)

readr::write_csv2(task1_dataset_triage, triage_path, na = "")

knitr::kable(task1_dataset_triage, format = "pipe", digits = 3)
```

## Plots by dataset

```{r}
#| results: asis
#| fig-width: 13
#| fig-height: 10

render_task1_dataset_sections(dataset_records)

```
